Think deep for reef resilience

### 2025-08-16 paper/paper_draft.qmd
Update carbonate budget plots to indicate mean number of years
Highlight the right-skewedness of the number of years above thresholds

Reef median depth has a moderate positive correlation with the number of years a reef
maintains coral cover above the assumed carbonate budget threshold required to sustain live
coral cover ($\theta_{0}$). Greater median depth is a key characteristic defining reefs that
sustain coral cover above $\theta_{0}$ [@fig-access-esm1-5-depth-carbonate]. Unsurprisingly,
the number of years above $\theta_0$ substantially decreases as $\theta_0$ is increased, as
does the Spearman's correlation. This is likely due to an increasing number of reefs being
unable to maintain coral cover above $\theta_0$ as the assumed threshold is increased, with
values **\[TI: Ben, could you clarify which values? Coral cover or years above
threshold?\]** becoming increasingly right-skewed. In contrast, log10-transformed total
connectivity strength ($\text{log10}(S)$) was found to have no correlation with the number
of years a reef maintains cover above the required thresholds
[@sfig-access-esm1-5-conn-carbonate] **\[TI: Ben, because we are comparing depth and
connectivity, this figure needs to be shown in the main text\]**. The correlation between
$\text{log10}(S)$ and $\theta_0$ slightly decreases as the assumed threshold for $\theta_0$
increases.

![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
2075. The assessed carbonate budget thresholds range from 10 to 20% of total reef area.
Bracketed x-axis values represent the Spearman's correlation between reef depth and the
number of years cover exceeds the carbonate budget threshold. Point colour represents the
median reef depth level in metres. Displays results from median time series using
ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/depth_carbonate_scatter.png){#fig-access-esm1-5-depth-carbonate
fig-align="center" width="14.82cm"}

@@

![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
2075. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
Bracketed x-axis values represent the Spearman's correlation between reef base-10 log of
total connectivity strength and the number of years cover exceeds the carbonate budget
threshold. The colour of each point represents the base-10 log of scaled reef total
connectivity strength. Displays results from median time series using
ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/log_total_strength_carbonate_scatter.png){#sfig-access-esm1-5-conn-carbonate
fig-align="center" width="14.82cm"}

>>>>

Reef median depth has a moderate positive correlation with the number of years a reef
maintains coral cover above the assumed carbonate budget threshold required to sustain live
coral cover ($\theta_{0}$). Greater median depth is a key characteristic defining reefs that
sustain coral cover above $\theta_{0}$ [@fig-access-esm1-5-depth-carbonate]. Unsurprisingly,
the number of years above $\theta_0$ substantially decreases as $\theta_0$ is increased, as
does the Spearman's correlation. This is likely due to an increasing number of reefs being
unable to maintain coral cover above $\theta_0$ as it is increased, with the distribution of
years above threshold becoming increasingly right-skewed
[@fig-access-esm1-5-depth-carbonate; @fig-access-esm1-5-conn-carbonate]. In contrast,
log10-transformed total connectivity strength ($\text{log10}(S)$) was found to have no
correlation with the number of years a reef maintains cover above the required thresholds
[@fig-access-esm1-5-conn-carbonate]. The correlation between $\text{log10}(S)$ and
$\theta_0$ slightly decreases as the assumed threshold for $\theta_0$ increases.

![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
2075. The assessed carbonate budget thresholds range from 10 to 20% of total reef area.
Bracketed x-axis values represent the Spearman's correlation between reef depth and the
number of years cover exceeds the carbonate budget threshold. Point colour represents the
median reef depth level in metres. Red points represent the mean number of years above a
carbonate threshold across reefs. Displays results from median time series using
ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/depth_carbonate_scatter.png){#fig-access-esm1-5-depth-carbonate
fig-align="center" width="14.82cm"}

![Number of years reef coral cover exceeds the carbonate budget threshold level from 2025 to
2075. The carbonate budget thresholds assessed range from 10 to 20% of total reef area.
Bracketed x-axis values represent the Spearman's correlation between reef base-10 log of
total connectivity strength and the number of years cover exceeds the carbonate budget
threshold. The colour of each point represents the base-10 log of scaled reef total
connectivity strength. Red points represent the mean number of years above a carbonate
threshold across reefs. Displays results from median time series using
ACCESS-ESM1-5.](../figs/ACCESS-ESM1-5/log_total_strength_carbonate_scatter.png){#fig-access-esm1-5-conn-carbonate
fig-align="center" width="14.82cm"}

**\[BG: I could combine these two plots into a single larger figure maybe, since it's quite
easy to see the contrasting depth vs connectivity patterns with colours even when zoomed
out.\]**

@@
